Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/BenchmarkResults.tex
chapter 4 feedback verwerkt

The accuracies of the Learning to Rank methods described in the following sections can only be compared within the benchmark and not between benchmarks for the following reasons:
\begin{enumerate}
\item Differences in feature sets between data sets detract from fair comparison
\item Although the \ac{NDCG} definition is unambiguous, Busa-Fekete et al. \cite{Busa-Fekete2012} found that \ac{NDCG} evaluation tools of benchmark data sets produced different scores
\end{enumerate}

@@

\subsubsection{Results}
\begin{table}[!h]
\begin{tabular}{l|lll}
 & OHSUMED & TD2003 & TD2004 \\
 \hline 
RankBoost & 0.4356 & 0.2851 & 0.4716 \\ 
Rank\acs{SVM} & 0.4411 & 0.3410 & 0.4201 \\ 
FRank & 0.4423 & 0.3357 & 0.4708 \\ 
ListNet & 0.4489 & 0.3743 & 0.4579 \\ 
AdaRank-\acs{MAP} & 0.4385 & 0.1940 & 0.4063 \\ 
AdaRank-\acs{NDCG} & 0.4369 & 0.2702 & 0.3878 \\ 
\acs{MHR} & 0.4423 &  &  \\ 
\end{tabular}
\caption{\acs{NDCG}@10 results of the baseline methods on LETOR 2.0}
\label{tab:letor2.0_results}
\end{table}
Table \ref{tab:letor2.0_results} shows the performance of the baseline methods on the data sets in the LETOR 2.0 collection. ListNet can be regarded as the winner of the comparison as it outperformed the other methods on two of the three data sets and ranked third on the third data set. \acs{MHR} was only evaluated on the OHSUMED data set, on which it performed second best, after ListNet.

@@

\subsection{WCL2R}
The WCL2R collection, released by Alc{\^a}ntara et al \cite{Alcantara2010}, contains of two data sets from the Chilean search engine TodoCL\footnote{www.todocl.cl}. Both data sets contain approximately 3 million documents. WCL2R is the only benchmark collection known that provides click-through data on user level. The collection contains 277,095 queries and logs of in total 1,5 million clicks by 16,829 users. The WCL2R paper provides evaluation results for the well-known Rank\ac{SVM} \cite{Herbrich1999,Joachims2002} and RankBoost \cite{Freund2003} algorithms. In addition two ranking methods developed at the same university of the WCL2R paper were evaluated: LAC \cite{Veloso2008} and a ranking algorithm based on \ac{GP} \cite{DeAlmeida2007}. Table \ref{tab:results_WCL2R} shows the performance of those algorithms on the WCL2R collection. No evaluations of other algorithms on the WCL2R collection are known.

>>>>

The accuracies of the Learning to Rank methods described in the following sections can only be compared within the benchmark and not between benchmarks for the following reasons:
\begin{enumerate}
\item Differences in feature sets between data sets detract from fair comparison
\item Although the \ac{NDCG} definition is unambiguous (note: there are two existing versions of \ac{NDCG}: J{\"a}rvelin and Kek{\"a}l{\"a}inen \cite{Jarvelin2002} and Burges et al. \cite{Burges2005}, but both are in itself defined unambiguously), Busa-Fekete et al. \cite{Busa-Fekete2012} found that \ac{NDCG} evaluation tools of different benchmark data sets produced different scores
\end{enumerate}
% TODO: hoe zit dit? Komt de vondst van Busa-Fekete door het Burges and Jarvelin verschil? %

@@

\subsubsection{Results}
\begin{table}[!h]
\begin{tabular}{l|lll}
 & OHSUMED & TD2003 & TD2004 \\
 \hline 
RankBoost & 0.4356 & 0.2851 & 0.4716 \\ 
Rank\acs{SVM} & 0.4411 & 0.3410 & 0.4201 \\ 
FRank & 0.4423 & 0.3357 & 0.4708 \\ 
ListNet & 0.4489 & 0.3743 & 0.4579 \\ 
AdaRank-\acs{MAP} & 0.4385 & 0.1940 & 0.4063 \\ 
AdaRank-\acs{NDCG} & 0.4369 & 0.2702 & 0.3878 \\ 
\acs{MHR} & 0.4423 & - & - \\ 
\end{tabular}
\caption{\acs{NDCG}@10 results of the baseline methods on LETOR 2.0}
\label{tab:letor2.0_results}
\end{table}
Table \ref{tab:letor2.0_results} shows the performance of the baseline methods on the data sets in the LETOR 2.0 collection. ListNet can be regarded as the winner of the comparison as it outperformed the other methods on two of the three data sets and ranked third on the third data set. \acs{MHR} was only evaluated on the OHSUMED data set, on which it performed second best, after ListNet.

@@

\subsection{WCL2R}
The WCL2R collection, released by Alc{\^a}ntara et al. \cite{Alcantara2010}, contains of two data sets originating from the Chilean search engine TodoCL\footnote{www.todocl.cl}. Both data sets contain approximately 3 million documents. WCL2R is the only benchmark collection known that provides click-through data on user level. The collection contains 277,095 queries and logs of in total 1,5 million clicks by 16,829 users. The WCL2R paper provides evaluation results for the well-known Rank\ac{SVM} \cite{Herbrich1999,Joachims2002} and RankBoost \cite{Freund2003} algorithms. In addition two ranking methods developed at the same university of the WCL2R paper were evaluated: LAC \cite{Veloso2008} and a ranking algorithm based on \ac{GP} \cite{DeAlmeida2007}. Table \ref{tab:results_WCL2R} shows the performance of those algorithms on the WCL2R collection. No evaluations of other algorithms on the WCL2R collection are known.
